---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sparseNumericHW6

<!-- badges: start -->
[![R-CMD-check.yaml](https://github.com/mdharnish/sparseNumericHW6/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/mdharnish/sparseNumericHW6/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of sparseNumericHW6 is to provide an S4 class implementation for sparse numeric vectors. This allows efficient storage and manipulation of numeric datasets that contain many zeros.

By storing only the non-zero values and their positions, sparse_numeric reduces memory usage while still supporting:

* Arithmetic (`+`, `-`, `*`)

* Coercion to and from base R numeric vectors

* Statistical summaries (`norm()`, `mean()`)

* Standardization (`standardize()`)

* Plotting of shared non-zero indices (`plot()`)

* Unit tests via **testthat** for all functionality

# Installation

You can install the development version of sparseNumericHW6 from GitHub using:

```{r}
devtools::install_github("mdharnish/sparseNumericHW6")
```

# Usage

Here is a basic example of how to create and manipulate sparse vectors:

```{r}
library(sparseNumericHW6)

# Create sparse vectors from standard numeric vectors
v1 <- sn_vec(c(1, 0, 2, 0, 0))
v2 <- sn_vec(c(0, 0, 3, 0, 4))

# Inspect object (prints internal structure)
v1
```

# Arithmetic

```{r}
v_sum  <- v1 + v2
v_prod <- v1 * v2

as(v_sum, "numeric")
as(v_prod, "numeric")
```

# Statistics

```{r}
v_std <- standardize(v1)
as(v_std, "numeric")
```

# Plotting

```{r}
plot(v1, v2)
```
